Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 250\,pc Halo

### 2021-02-05 cluster_paper/ms.tex
update paper

\newcommand{\ncalibration}{9{,}619{,}784} % /nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/counts/check_sum, 2021.02.02
\newcommand{\nnbhd}{13{,}843\ } % make_compstar_NGC_2516_sourcelist.py
\newcommand{\nnbhdcaliblc}{10{,}314\ } % make_compstar_NGC_2516_sourcelist.py
\newcommand{\nnbhdcalibstar}{2{,}212\ } % make_compstar_NGC_2516_sourcelist.py

@@

% Context, aims, methods, results, conclusions.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters.  The
  stars in these ``halos'' could have escaped from the cores of the
  cluster, or they could be remnants of a star formation complex that
  has since dispersed.  They could also be field stars---false
  positives from overly aggressive clustering algorithms.  In this
  study, we focus on a 250\,pc halo reported
  around the $\approx$120\,Myr open cluster NGC\,2516.  The classical
  tidal radius of the cluster is {\bf $\sim$XX\,pc}.  Using photometry
  from Gaia, rotation periods from TESS, and lithium measurements from
  Gaia-ESO and GALAH, we find that the halo of NGC\,2516 is real and
  coeval with the core.  Two in three kinematically selected halo
  members 25-250\,pc from the cluster center show rotation periods
  consistent with a gyrochronological age of 120\,Myr.  Stars in the
  inner 25\,pc show higher period detection rates than the
  halo (73\% vs.\ 66\%), but both vastly exceed our field star
  comparison sample ({\bf XX\%}).  The rotation rate and lithium abundance
  are also anti-correlated at fixed stellar mass, as is the case with
  comparable clusters.  This work expands the set of confirmed
  NGC\,2516 members by a factor of $\approx$2, and quantifies the
  degree to which Gaia-based analyses can identify dispersed stellar
  populations against a background of field star contaminants.  We
  highlight the implications for spectroscopic survey targeting, open
  cluster dispersal, and planet searches around young stars.
\end{abstract}
% Rotators < 25pc : 0.72929 +/- 0.00013
% Rotators > 25pc : 0.66172 +/- 0.00023

>>>>

\newcommand{\ncalibration}{9{,}619{,}784\ } % /nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/counts/check_sum, 2021.02.02
\newcommand{\nnbhd}{13{,}843\ } % make_compstar_NGC_2516_sourcelist.py
\newcommand{\nnbhdcaliblc}{10{,}314\ } % make_compstar_NGC_2516_sourcelist.py
\newcommand{\nnbhdcalibstar}{2{,}212\ } % make_compstar_NGC_2516_sourcelist.py

@@

% Context, aims, methods, results, conclusions.
\begin{abstract}
  Recent analyses of the Gaia data have reported the existence of
  diffuse stellar populations surrounding nearby open clusters.  The
  stars in these ``halos'' could have escaped from the cores of the
  cluster, or they could be remnants of a star formation complex that
  has since dispersed.  They could also be field stars---false
  positives from overly aggressive clustering algorithms.  In this
  study, we focus on a 250\,pc halo reported
  around the $\approx$120\,Myr open cluster NGC\,2516.  The classical
  tidal radius of the cluster is {\bf $\sim$XX\,pc}.  Using photometry
  from Gaia, rotation periods from TESS, and lithium measurements from
  Gaia-ESO and GALAH, we find that the halo of NGC\,2516 is real and
  coeval with the core.  Two in three kinematically selected halo
  members 25-250\,pc from the cluster center show rotation periods
  consistent with a gyrochronological age of 120\,Myr.  Stars in the
  inner 25\,pc show higher period detection rates than the
  halo (73\% vs.\ 66\%), but both vastly exceed our field star
  comparison sample ({\bf XX\%}).  The rotation rate and lithium abundance
  are also anti-correlated at fixed stellar mass, as is the case with
  comparable clusters.  This work expands the set of confirmed
  NGC\,2516 members by a factor of $\approx$2, and quantifies the
  degree to which Gaia-based analyses can identify dispersed stellar
  populations against a background of field star contaminants.  We
  highlight implications for spectroscopic survey targeting, open
  cluster dispersal, and planet searches around young stars.
\end{abstract}
% Rotators < 25pc : 0.72929 +/- 0.00013
% Rotators > 25pc : 0.66172 +/- 0.00023
